Group 1: Predicting the Outcomes of Tennis Tournaments

### 2019-12-17 Group1Prez.Rmd
Cleaned Up

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab("Players") + 
  ylab("Number of Times Won") +
  ggtitle("Which Player Won the Tournament?",
          subtitle = "2002 Women's US Open")

>>>>

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") + 
  ylab("Number of Times Won") +
  ggtitle("Which Player Won the Tournament?",
          subtitle = "2002 Women's US Open")
